---
title: "Data Visualization"
author: "Christian Gao"
date: "6/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## R Markdown

**1.** I described 7 possible things you can visualize, what are they?

**2.** Describe uses of a diverging bar, when is it appropriate, draw one.

A diverging stacked bar chart allows you to show two or more segments in multiple category bars compared to a goal value. It shows the distributions of certain factors within certain groups or populations.

```{r diverging bar}
ggplot(mtcars, aes(x=carb, y=mpg, fill=gear)) + 
  geom_bar(stat="identity") + coord_flip()
```

**3.** Describe uses of a spline chart, when is it appropriate, draw one.

```{r spline}
n <- 10
d <- data.frame(x = 1:n, y = rnorm(n))
ggplot(d,aes(x,y)) + geom_point() + 
  geom_line(data=data.frame(spline(d,n=n*10)))
```

**4.** Describe uses of an area chart, when is it appropriate, draw one.

Area charts are used to represent cumulated totals using numbers or percentages. It is often used to show the changes of these values over time.

**5.** Describe uses of a scatterplot, when is it appropriate, draw one.

Scatterplots are used to describe how much one variables is associated to another. It is used to visualize the joint interactions of two variables.

**6.** Describe uses of a bubble chart, when is it appropriate, draw one.

Bubble chart is just like scatterplot except the size of the point indicates the size of an attribute for that observation.

**7.** Describe uses of a heatmap,  when is it appropriate, draw one.

Distribution of a density accross a geographic or 2D Location.

**8.** Describe uses of a linechart, when is it appropriate, draw one.

Like scatterplot except points are ordered. Can be used to describe time.

**9.** Name the major components of the grammar of graphics.

stupid

**10.** Using ggplot and the iris dataset, what is the command for a scatterplot of Sepal Length and Width colored by species with dot area scaled by the difference between petal width and length?

**11.** !!!Describe the major components of a Shiny application

**12.** !!!Why won't this shiny code run:

```
library(shiny)

shinyUI(fluidPage(

  # Application title
  titlePanel("Old Faithful Geyser Data"),

  # Sidebar with a slider input for number of bins
  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30)
    ),

    # Show a plot of the generated distribution
    mainPanel(
      plotOutput("distPlot")
    )
  )
))

shinyServer(function(input, output) {
  
  output$plotOutput <- renderPlot({
    
    # generate bins based on input$bins from ui.R
    x    <- faithful[, 2]
    bins <- seq(min(x), max(x), length.out = input$bins + 1)
    
    # draw the histogram with the specified number of bins
    hist(x, breaks = bins, col = 'darkgray', border = 'white')
    
  })
  
})
```
